Online {\IterComp}

### 2017-11-17 motivation.tex
motivation minor
motivation fix

    \paragraph{Representative input sets are hard to create.} For developers to create artificial input sets, they first need to know how
    their application is actually being used. This is not always easy or even possible. Then, they need to create data that will trigger a
    similar behavior as when the application is used by users. This needs a deep knowledge of the potential user behavior and
    considerable effort. This will have to be a continuous work in progress, to handle changes in the way the application is used. In some
    areas, such as mobile computing, where developers do not traditionally optimize their applications or provide inputs for performance
    testing, depending on them to provide inputs is a suboptimal choice.

@@

\begin{table}[t]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Metric} & \textbf{Average Speedup/Slowdown} & \textbf{IPC} \\ \hline
\rowcolor{Gray} Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
\rowcolor{Gray}1/Runtime                    & 3\% slowdown                                  & {-}   \\ \hline
\end{tabular}
\caption{Comparison of iterative compilation guided by different metrics.
The oracle is guided by the average speedup over \texttt{-O3} on all inputs.
For IPC and runtime, each optimization was evaluated on a different input.
}
\end{table}

>>>>

    \paragraph{Representative input sets are hard to create.} For developers to create artificial input sets, they first need to know how
    their application is actually being used. This is not always easy or even possible. Then, they need to create data that will trigger a
    similar behavior as when the application is used by users. This needs a deep knowledge of the potential user behavior and
    considerable effort. This will have to be a continuous work in progress, to handle changes in the way the application is used. In some
    areas, such as mobile computing, where developers do not traditionally optimize their applications or provide inputs for performance
    testing, depending on them to provide inputs is unrealistic.

@@

\begin{table}[t]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Metric} & \textbf{Speedup/Slowdown} & \textbf{IPC} \\ \hline
\rowcolor{Gray} Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
\rowcolor{Gray}1/Runtime                    & 3\% slowdown                                  & {-}   \\ \hline
\end{tabular}
\caption{Comparison of iterative compilation guided by different metrics.
The oracle is guided by the average speedup over \texttt{-O3} on all inputs.
For IPC and runtime, each optimization was evaluated on a different input.
}
\end{table}
